Format for lefse and run on the classes CR and tox

### 2019-11-04 scripts/18_lefse_metaphlan2_CR_tox.Rmd
update

```{r}
# plot the cladogram   
pheno_combi %>% 
  mutate(lefse_res = str_glue('../data/lefse_input/spp_abundace_{combi}res'),
         cla_png = str_glue('../figs/cladogram/spp_abundace_lefse_{combi}png'),
         cmd = str_glue('plot_cladogram.py {lefse_res}  {cla_png}  --dpi 300 --format png --title {combi} --label_font_size 3')) %>% 
  select(cmd) %>% 
  write_csv('plotting_cladogram_spp.sh', col_names = F)
```

@@

```{bash}
# this is the bash script to do the actual concatenation 
bash cat_combi_spp.sh
bash format_input_spp.sh
bash run_lefse_spp.sh
bash plotting_de_feature_spp.sh
plotting_cladogram_spp.sh
```

>>>>

```{r}
# plot the cladogram   
pheno_combi %>% 
  mutate(lefse_res = str_glue('../data/lefse_input/spp_abundace_{combi}res'),
         cla_png = str_glue('../figs/cladogram/spp_abundace_lefse_{combi}png'),
         cmd = str_glue('plot_cladogram.py {lefse_res}  {cla_png}  --dpi 300 --format png --title {combi} --label_font_size 4')) %>% 
  select(cmd) %>% 
  write_csv('plotting_cladogram_spp.sh', col_names = F)
```

@@

```{bash}
# this is the bash script to do the actual concatenation 
bash cat_combi_spp.sh
bash format_input_spp.sh
bash run_lefse_spp.sh
bash plotting_de_feature_spp.sh
bash plotting_cladogram_spp.sh
```
